% A personal resume based on the document style created by Michael DeCorte

\documentclass{res}
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page

\begin{format}
	\employer{l}\location{r}\\
		\title{l}\dates{r}\\
		\body\\
	\end{format}

\begin{document}

\name{Dylan Herts\\[12pt]}
% the \\[12pt] adds a blank
% line after name

\address{8 Douglass St. \#3F\\Cambridge, MA 02139}
\address{dylan@herts.io \\ (216) 288-2768}

\begin{resume}

\section{EDUCATION}
        \employer{\textbf{Harvard Law School}}
        \title{J.D., \textit{magna cum laude}}
        \location{Cambridge, MA}
        \dates{May 2019}
        \begin{position}
        \end{position}

        \employer{\textbf{Amherst College}}
        \title{Bachelor of Arts, \textit{summa cum laude}}
        \location{Amherst, MA}
        \dates{May 2013}
        \begin{position}
        \end{position}

\section{EXPERIENCE}
    \employer{\textbf{Hon. F. Dennis Saylor IV (D. Mass.)}}
    \title{Judicial Law Clerk}
    \location{Boston, MA}
    \dates{2019 -- Present}
    \begin{position}
    \end{position}

    \employer{\textbf{Davis Polk \& Wardwell}}
    \title{Summer Law Clerk}
    \location{New York, NY}
    \dates{Summer 2018}
    \begin{position}
        Drafted legal memoranda on choice-of-law issues in a commercial litigation matter. Interviewed affiants and prepared draft affidavits for a pro bono immigration proceeding. Researched New York law on punitive damages.
    \end{position}

    \employer{\textbf{U.S. Dep't of Justice, Antitrust Division}}
    \title{Volunteer Intern}
    \location{Washington, D.C.}
    \dates{Summer 2017}
    \begin{position}
        Drafted legal memoranda on anticompetitive effects theories in telecommunications mergers and relative effectiveness of available merger remedies. Reviewed two Hart-Scott-Rodino premerger notification filings and drafted ‘no interest’ recommendation memoranda, which section management approved.
    \end{position}

    \employer{\textbf{Cornerstone Research}}
    \title{Analyst / Senior Analyst}
    \location{New York, N.Y.}
    \dates{2013 -- 2016}
    \begin{position}
        Provided financial and economic analysis for attorneys litigating securities, antitrust, defamation, and labor matters. Assisted expert witnesses in designing analyses, drafting and finalizing expert reports, and preparing for depositions. Estimated consumer demand to predict quality-adjusted price impacts from proposed telecommunications merger. Performed econometric analysis to predict counterfactual sales in food libel action.
    \end{position}

    \employer{\textbf{Infosys}}
    \title{InStep Intern}
    \location{Hyderabad, India}
    \dates{Summer 2012}
    \begin{position}
        Conducted research on modern cybersecurity in social network environments and devised countermeasures against common exploits for the second-largest IT services company in India.
    \end{position}





\section{Personal}
    Loves running, hiking, jazz, ice cream, and speculative fiction.

\end{resume}
\end{document}
